### 2024-08-26 mycv/subs/papers.tex
Updates

  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}

@@

  {in-press}

>>>>

  {\ref{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}}

@@

  {Vol. 181, 104098, 2024}
